---
title: "Stats 20, W23 -- Homework 3"
author: "Haojie Liu -- 905943123"
date: "`r format(Sys.Date(), '%D')`"
output:
  html_document:
    toc: yes            # creates table of contents
    toc_depth: 4        # toc will include headers <= ####
    toc_float: yes      # toc always on left of page
    code_folding: show  # allows hiding of code
---

## Question 1

### (a)
<!-- USE THE CODE CHUNK BELOW -->
```{r Question 1a}

commute_times <- c(14,12,20,19,15,20,28,20,20,18)
is_no_more<-commute_times>(mean(commute_times)-sd(commute_times)) & commute_times<(mean(commute_times)+sd(commute_times))
which(!is_no_more)
commute_times[which(!is_no_more)]

```
<!-- ENTER YOUR EXPLANATION BELOW (USING INLINE R AS YOU WILL) -->
The 1, 2 and 7 day are not with in one standard deviation of the mean. Those times are 14, 12, 28
### (b)
<!-- USE THE CODE CHUNK BELOW -->
```{r Question 1b}
which(is_no_more)
commute_times[which(is_no_more)]
```
<!-- ENTER YOUR EXPLANATION BELOW (USING INLINE R AS YOU WILL) -->
The 3,4,5,6,8,9 and 10 day are with in one standard deviation of the mean. Those times are 20, 19, 15, 20, 20, 20 and 18
### (c)
<!-- USE THE CODE CHUNK BELOW -->
```{r Question 1c}
length(which(is_no_more))/length(commute_times)
```
<!-- ENTER YOUR EXPLANATION BELOW (USING INLINE R AS YOU WILL) -->
The proportion of Andy have a commute time that was within one standard deviation of the mean commute time is 0.7.

## Question 2

```{r Question 2}
NA & TRUE
NA & FALSE
NA | TRUE
NA | FALSE
```
<!-- ENTER YOUR EXPLANATION BELOW, FEEL FREE TO EDIT THE ABOVE CODE CHUNK -->
For NA&TRUE. When we have a missing value 'NA', the system can make sure if the statement is true or not. Therefore, the system out put NA because it can't be TRUE or FALSE.
For NA&FALSE. As we mentioned in the first one, the system now knows that it is FALSE anyway, no matter what the other statements is. So it's FALSE
For NA&TRUE. We only need one statement claimed as TRUE in '|', then the system can understand that this can be claimed as TRUE.
For NA|FALSE. The system having problem to determine if the statement is TRUE with NA. Even the right hand side is FALSE, we still need to have both statement there to be clarify to the system. Or it will out put it as "unknow" or 'NA'.

## Question 3

<!-- PUT YOUR get_minimum_coins() FROM HW 1 HERE -->
```{r Question 3 background} 
get_minimum_coins<- function(n){
  n<-n*100
  count <- 0
  count <- count+(n%/%25)

  n <- n%%25
  count <- count+(n%/%10)

  n <- n%%10
  count <- count+(n%/%5)
  
  n <- n%%5
  count <- count+(n%/%1)
  count
}
```

### (a)
<!-- ENTER YOUR ANSWER BELOW -->
The function get_minimum_coins is not vectorized because we calculated every single value turn by turn, instead of calculate it as a vector.
<!-- USE THE CODE CHUNK BELOW IF YOU'D LIKE -->
```{r Question 3a}

```

### (b)
<!-- ENTER YOUR ANSWER BELOW, IT CAN BE JUST COMMANDs; NO NEED TO STORE OBJECTs -->
```{r Question 3b}
seq(0.01,1, by = 0.01)[which(get_minimum_coins(seq(0.01,1, by = 0.01))==max(get_minimum_coins(seq(0.01,1, by = 0.01))))]
```

## Question 4

### (a)
<!-- CREATE THE FUNCTION IN THE CODE CHUNK BELOW -->
<!-- NAME THE FUNCTION AND ITS INPUTS EXACTLY AS STATED IN THE ASSIGNENT -->
<!-- PLAN OUT YOUR APPROACH BEFORE YOU START CODING ANY FUNCTION. -->
```{r Question 4a}
my_min<-function(a, na.rm=FALSE){
  x<-a[1];
  if (na.rm==TRUE){
    a<-a[which(is.na(a)==FALSE)]
  }
  
  for (i in seq_along(a)){
    if(is.na(a[i])||is.na(x)){
      x <- NA
    }
    else if(a[i]<x){
      x<-a[i]
    }
  }
  x
  
}
```

### (b)
<!-- USE THE CODE CHUNK BELOW, IT CAN BE JUST COMMANDs; NO NEED TO STORE OBJECTs -->
```{r Question 4b}

my_min(c(4, 1, 0, 2, -3, -5, -4))
my_min(c("bears", "beets", "Battlestar Galactica"))
my_min(7)
my_min(c("Pawnee", "rules", "Eagleton", NA), na.rm = TRUE)
my_min(c("Pawnee", "rules", "Eagleton", NA), na.rm = FALSE)
my_min(NA, na.rm = TRUE)
my_min(NA, na.rm = FALSE)

```


## Question 5

### (a)
<!-- USE THE CODE CHUNK BELOW -->
```{r Question 5a}

fib1 <- 1
full_fib <- (fib1)
while (fib1 < 500) {
  full_fib <- c(full_fib, fib1)
  fib1 = full_fib[length(full_fib)-1]+fib1
} 
full_fib


```

### (b)
<!-- USE THE CODE CHUNK BELOW -->
```{r Question 5b}

full_fib <- c(1,1)
while ((full_fib[length(full_fib)]+full_fib[length(full_fib)-1]) < 500) {
  
  full_fib<-c(full_fib, full_fib[length(full_fib)]+full_fib[length(full_fib)-1])
  
} 
full_fib
```

### (c)
<!-- USE THE CODE CHUNK BELOW -->
```{r Question 5c}

while ((full_fib[length(full_fib)]+full_fib[length(full_fib)-1]) < 1000000000) {
  
  full_fib<-c(full_fib, full_fib[length(full_fib)]+full_fib[length(full_fib)-1])
  
} 
length(full_fib)

```
<!-- ENTER YOUR EXPLANATION BELOW (USING INLINE R AS YOU WILL). ONE SENTENCE OR 'MY ANSWER IS __' IS FINE. -->

## Question 6
<!-- USE THE CODE CHUNK BELOW -->
```{r Question 6}


jerry <- 2:(8 * (5 %% 3)^-2):(7 > 2)
jerry



```

## Question 7

### (a)
<!-- CREATE THE FUNCTION IN THE CODE CHUNK BELOW -->
<!-- NAME THE FUNCTION AND ITS INPUTS EXACTLY AS STATED IN THE ASSIGNENT -->
<!-- PLAN OUT YOUR APPROACH BEFORE YOU START CODING ANY FUNCTION. -->
```{r Question 7a}
my_ifelse <- function(test,yes,no){

  no[test]<-yes[test]
  no
  
}

```

### (b)
<!-- USE THE CODE CHUNK BELOW -->
```{r Question 7b}
x <- (1:10)*pi
my_ifelse(x %% 1 >= 0.5, x %/% 1 + 1, x %/% 1)
```

### (c)
<!-- CREATE THE FUNCTIONs IN THE CODE CHUNK BELOW -->
<!-- NAME THE FUNCTIONs AND THEIR INPUTS EXACTLY AS STATED IN THE ASSIGNENT -->
<!-- PLAN OUT YOUR APPROACH BEFORE YOU START CODING ANY FUNCTION. -->
```{r Question 7c}

my_abs<- function(x){
  
  my_ifelse(x<0, x-x-x, x)
  
}

my_sign<- function(x){
  
  my_ifelse(x<0,-1,x)
  
}

```
<!-- REMINDER TO USE my_ifelse() TO WRITE THE FUNCTIONS. THERE ARE OTHER WAYS TO WRITE THESE FUNCTIONS WITHOUT USING my_ifelse() BUT PLEASE FOLLOW THE DIRECTIONS. -->

## Question 8

### (a)
<!-- CREATE THE FUNCTIONs IN THE CODE CHUNK BELOW -->
<!-- NAME THE FUNCTIONs AND THEIR INPUTS EXACTLY AS STATED IN THE ASSIGNENT -->
<!-- PLAN OUT YOUR APPROACH BEFORE YOU START CODING ANY FUNCTION. -->
```{r Question 8a}
merge <- function(left,right){
  
  merged <- c();
  while(length(left)>0){
    
    if(length(right)>0){
      
      if(left[1]<right[1]){
        merged<-c(merged,left[1]);
        left<-left[-1];
      }else{
        merged<-c(merged,right[1]);
        right<-right[-1];
      }
      
    }else{
      
      merged <- c(merged,left);
      left <- c();
      
    }
  }
  c(merged,right);
}

merge_sort<- function(x){
  
  if(length(x)>1){
    
    left<-x[1:(length(x)/2)];
    right<-x[-(1:(length(x)/2))];
    sort_left<-merge_sort(left);
    sort_right<-merge_sort(right);
    x<-merge(sort_left,sort_right);
  }
  x
}

```

### (b)
<!-- USE THE CODE CHUNK BELOW, IT CAN BE JUST COMMANDs; NO NEED TO STORE OBJECTs -->
```{r Question 8b}
merge_sort(numeric(0))
merge_sort(7)
merge_sort(1:10)
```

## Question 9
<!-- MAKE SURE dna.RData IS IN THE SAME DIRECTORY (FOLDER) AS THIS .RMD -->
```{r Question 9 background}
load("dna.RData")

```

### (a)
<!-- CREATE THE FUNCTION AND TEST IT AS ASKED IN THE CODE CHUNK BELOW -->
<!-- NAME THE FUNCTION AND ITS INPUTS EXACTLY AS STATED IN THE ASSIGNENT -->
<!-- PLAN OUT YOUR APPROACH BEFORE YOU START CODING ANY FUNCTION. -->
```{r Question 9a}
locate_motif <- function(strand, motif){
  
  for (i in (length(strand)-length(motif))){
    
    if(strand[i]==motif[i]){
      
      for(j in length(motif)){
        
      }
      
    }
    
  }
  
}

```

### (b)
<!-- CREATE THE FUNCTION AND TEST IT AS ASKED IN THE CODE CHUNK BELOW -->
<!-- NAME THE FUNCTION AND ITS INPUTS EXACTLY AS STATED IN THE ASSIGNENT -->
<!-- PLAN OUT YOUR APPROACH BEFORE YOU START CODING ANY FUNCTION. -->
```{r Question 9b}

```
